---
title: "Data Product Project 1"
author: "KevLee"
date: "1/27/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem Description
Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

## Load Packages
```{r}
library(leaflet)
```
```{r}
library(htmltools)
```

```{r}
library(tidygeocoder)
```

## Import data

Use R Built-in data set USArrests
```{r}
data('USArrests')
data <- USArrests
```
Organize data

```{r}
data <- data.frame(cbind(State = rownames(data),data))
rownames(data) <- 1:nrow(data)
data$TT_Arrest <- data$Murder + data$Assault +data$UrbanPop +data$Rape
```
load state info data
```{r}
state <- read.csv('statelatlong.csv')
```
join two datasets
```{r}
data <- merge(data, state, by.x = 'State' , by.y = 'City')
```
## Leaflet Map

```{r}
map <- data %>%
  leaflet() %>%
  addTiles() %>%
  setView(lat = 40, lng = -95, zoom =4) %>%
  addMarkers(popup = 'Murder') %>%
  addCircles(weight=1,radius = data$Murder*30000)

```
```{r}
map
```
